Paper on the carbonate chemistry at Ny-Ålesund

### 2020-12-07 paper.Rmd
dunno

d_all <- readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

tmp visdat::vis_miss(tmp)
gg_miss_var(tmp, facet = quarter)

>>>>

d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
  replace(., is.na(.), NA) # replace NaN by NA everywhere
```

@@

visdat::vis_miss(zz)
#gg_miss_var(zz, facet = quarter)
